---
title: "Supplemental Code for Toxicon Correspondence (iVAMP)"
author: "Ul-Hasan et al"
output: word_document
---

Contributors to literature review (by order): SU, ERR, TJC, VH, SAT, SAM, CNK, EES, AJS, AMR
Contributors to code: SU 

Methods:

Web of Science search of all 73,038,152 peer-reviewed publications
TITLE: (venom* AND microb*) OR TITLE: (venom* AND bacteri*) OR TITLE: (venom* AND fung*) OR TITLE: (venom* AND virus*)

Timespan=All years. Indexes=SCI-EXPANDED, SSCI, A&HCI, CPCI-S, CPCI-SSH, BKCI-S, BKCI-SSH, ESCI, CCR-EXPANDED, IC.


Results:                       159 hits (140 in analysis)
  Corrections removed           2
  News articles removed         2
  Abstract removed              15 
  Irrelevant articles           14 (see line 98)
> Create Citation Report > Export Data (Save to Excel File) > Delete first 28 rows (manually) > Create "Article" column to number all articles > Save as .csv for processing
  
Sum of the Times Cited        2589
Average Citations per Item    18.49
h-index                       29

Upload Web of Science search output and clean-up
```{r}

### Upload data
# install.packages("RCurl")
library("RCurl") # package needed for downloading data from Github repo
# packageVersion("RCurl") # v1.95.4.12 

Raw <- read.csv(text=getURL("https://raw.githubusercontent.com/ivamp-consortium/ToxiconX_Correspondence/master/Web-of-Science_Raw-Jun22-2019.csv"))

### Process Raw to Clean data
# Make the following columns all lower case
Raw$Title <- tolower(Raw$Title) 
Raw$Authors <- tolower(Raw$Authors)
Raw$Book.Editors <- tolower(Raw$Book.Editors)
Raw$Source.Title <- tolower(Raw$Source.Title)

# install.packages("tidyverse")
library(tidyverse)
# packageVersion("tidyverse") # v1.2.1

# Add an Article column that numbers each row incrementally
Raw <- tibble::rowid_to_column(Raw, "Article")

# Remove punctuation from these 
Title <- Raw$Title %>%
  str_replace_all('[^a-z0-9]+', ' ')
Title <- data.frame(Title)
Authors <- Raw$Authors %>%
  str_replace_all('[^a-z0-9]+', ' ')
Authors <- data.frame(Authors)
Book.Editors <- Raw$Book.Editors %>%
  str_replace_all('[^a-z0-9]+', ' ')
Book.Editors <- data.frame(Book.Editors)
Source.Title <- Raw$Source.Title %>%
  str_replace_all('[^a-z0-9]+', ' ')
Source.Title <- data.frame(Source.Title)

NoPunc <- cbind(Title, Authors, Book.Editors, Source.Title)
NoPunc$Article <- Raw$Article
NoPunc_Annot <- merge(NoPunc, Raw, by = "Article")
NoPunc_Annot <- NoPunc_Annot[,-c(6:9)] # drops columns with punctuation

# Write as .csv file and manually clean up / annotate
# Add Microbe, Topic, and Animal columns (note articles are re-numbered by year)
write.csv(NoPunc_Annot, "Manual_Clean-up.csv")
# To the viewer: There is certainly an automated way to do this, but we concluded it was more direct to approach manually based on our expertise. We strongly encourage and welcome recommendations to better automate this process.

Clean <- read.csv(text=getURL("https://raw.githubusercontent.com/ivamp-consortium/ToxiconX_Correspondence/master/Supp_Tab1_Web-of-Science_Clean-Jun22-2019.csv"))

```

Figure 1a-c
```{r}

# install.packages("wordcloud")
library(wordcloud)
# packageVersion("wordcloud") # v2.6

# Note that words may not show up for a word cloud if RStudio screen is too small (expand manually if 'transformation drops documentstransformation drops documents' error shows up)

# Figure 1a: Microbe categories
Microbe = wordcloud(Clean$Microbe) 
Microbe # None category are studies with term 'microb*' that refer to wasp microbracon
dev.copy(png, "Figure1a_Microbe_140-articles.png")
dev.off() 

Microbe_only$Topic<-as.character(Microbe_only$Topic)
# Remove all articles for "none" category
Microbe_only = subset(Clean, !Microbe=="none") # 14 articles removed (126 remain)
# Figure 1b: Article topic
Topic = wordcloud(Microbe_only$Topic, col = "#8D221D") 
Topic # 90 antimicrobial, 14 symbiosis
dev.copy(png, "Figure1b_Topic_126-articles.png")
dev.off() 

(90/126)*100 # 71 % antimicrobial
(14/126)*100 # 11 % symbiosis

# Figure 1c: Animal of origin
Animal = wordcloud(Microbe_only$Animal, col = "#8D221D") 
Animal # 72 are from snakes
dev.copy(png, "Figure1c_Animal_126-articles.png")
dev.off() 

(72/126)*100 # 57 % from snakes, 41% from intevertebrates

```
